ASA24 Preprocessing

### 2022-03-24 Rmarkdown/preprocessing/ASA24_Preprocessing_211111.Rmd
limit to useful code

Many of these variables do not have a normal distribution. We will use this data to run parametric statistics so go ahead and transform key variables for future use.

@@

Little exploration below. Pay no mind.
```{r}
# Count number of subjects with 2 vs 3 recalls
dat2_count <- dat2[complete.cases(dat2$lang_tnf),] # 384
dat3_count <- dat3[complete.cases(dat3$lang_tnf),] # 378
dat4_count <- dat4[complete.cases(dat4$lang_tnf),] # 347

# What is the distribution of meat intake across the recalls?
summary(dat2$pf_meat_totals)
summary(dat3$pf_meat_totals)
summary(dat4$pf_meat_totals)

summary(dat2$pf_curedmeat_totals)
summary(dat3$pf_curedmeat_totals)
summary(dat4$pf_curedmeat_totals)

t.test(dat2$pf_curedmeat_totals, dat4$pf_curedmeat_totals) # not different, good

# List of TMAO subjects

# List of subjects with at least 2 recalls and TMAO data

# List of subjects with at least 3 recalls and TMAO data
```

>>>>

Many of these variables do not have a normal distribution. They have been tested in an external program for the best transformation. We will use this data to run parametric statistics so go ahead and transform key variables for future use.

@@
